---
title: "DataScouteR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DataScouteR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

DataScouteR is an R package for football scouting and player evaluation.
It provides Football Manager–style (1–20) ratings derived from advanced
performance metrics, scaled for intuitive interpretation.

The current version focuses on goalkeepers, offering a clean and simple
interface to access precomputed scouting data.

## Installation

The package can be installed directly from GitHub:

```{r}
install.packages("remotes")
remotes::install_github("machoude/DataScouteR", subdir = "DataScouteR")
```

##  Loading the package


```{r setup}
library(DataScouteR)
```

## Goalkeeper scouting data

Goalkeeper data can be accessed using the `get_gk()` function.

```{r}
gk <- get_gk()
head(gk)
```

## Interpreting the ratings

All performance metrics are scaled to a 1–20 range, similar to Football
Manager ratings, for easier interpretation.

A value around 10 represents an average performance level, while values
above 12 indicate above-average quality for the given role. Higher values
reflect stronger relative performance, adjusted across leagues and
competitions.

## Data source

The underlying performance data are sourced from FBref.
Metrics are processed, standardized, and rescaled for scouting purposes.
DataScouteR is not affiliated with FBref.

## Future development

Future versions of DataScouteR will expand coverage to additional
positions, following the same interface and design principles.
